---
title: "Practical Machine Learning Assignment"
author: "Andrew Szwec"
date: "Tuesday, April 21, 2015"
output: html_document
---

This is a the Coursera Practical Machine Learning Assignment.

## Load Data 
```{r}
# Set environment Variables to download files from BioConductor using the proxy
Sys.setenv(http_proxy="http://proxy.au.deloitte.com:80/", http_proxy_user="aszwec:password") 


# Load Data
file1 <- 'C:/Users/aszwec/Documents/Coursera/pracML/assignment/pml-training.csv'
file2 <- 'C:/Users/aszwec/Documents/Coursera/pracML/assignment/pml-testing.csv'

raw_train <- data.frame(read.csv(file1, header=TRUE))
raw_test <- data.frame(read.csv(file1, header=TRUE))

head(raw_train)
names(raw_train)
ncol(raw_train)

names(raw_train)[grepl('^gyros\\w+' , names(raw_train))]


```

## Data Exploration

```{r, echo=FALSE}


library(plyr)
counts <- count(raw_train, var='classe')

require(ggplot2)
qplot(counts$classe, counts$freq, geom='bar', stat="identity", main='Number of Samples per Test', xlab ='Test Case', ylab='Count', fill=counts$classe)

qplot(raw_train$pitch_belt, raw_train$roll_belt, geom='point', colour=raw_train$classe )

qplot(raw_timestamp_part_1, gyros_arm_x, geom='point', facets=.~classe , data=raw_train, colour=raw_train$classe )
# 
# qplot(raw_timestamp_part_1, gyros_arm_y, geom='point', facets=.~classe , data=raw_train, colour=raw_train$classe )
# 
# qplot(raw_timestamp_part_1, gyros_arm_z, geom='point', facets=.~classe , data=raw_train, colour=raw_train$classe )


# Look at what exercise each participant carried out? They all carried out each exercise
count(raw_train, vars=c('user_name','classe') )


```



## Train 
```{r}
require(caret)

# find non zero columns
nzv <- nearZeroVar(raw_train, saveMetrics=TRUE)

# Number of columns in train = 160
nrow(nzv)
# Number of columns in train that are not near zero = 100
nrow(nzv[which(nzv$nzv==FALSE),])

# Extract non zero col names
nz_cols <- nzv[which(nzv$nzv==FALSE),]

# Drop X column as this is just a row index
keeps <- data.frame(col_name = rownames(nz_cols))

?subset

remaining_cols <- subset(raw_train , select=c(X ,user_name ,raw_timestamp_part_1 ,raw_timestamp_part_2 ,cvtd_timestamp ,num_window, new_window ,roll_belt ,pitch_belt ,yaw_belt ,total_accel_belt ,max_roll_belt ,max_picth_belt ,min_roll_belt ,min_pitch_belt ,amplitude_roll_belt ,amplitude_pitch_belt ,var_total_accel_belt ,avg_roll_belt ,stddev_roll_belt ,var_roll_belt ,avg_pitch_belt ,stddev_pitch_belt ,var_pitch_belt ,avg_yaw_belt ,stddev_yaw_belt ,var_yaw_belt ,gyros_belt_x ,gyros_belt_y ,gyros_belt_z ,accel_belt_x ,accel_belt_y ,accel_belt_z ,magnet_belt_x ,magnet_belt_y ,magnet_belt_z ,roll_arm ,pitch_arm ,yaw_arm ,total_accel_arm ,var_accel_arm ,gyros_arm_x ,gyros_arm_y ,gyros_arm_z ,accel_arm_x ,accel_arm_y ,accel_arm_z ,magnet_arm_x ,magnet_arm_y ,magnet_arm_z ,max_picth_arm ,max_yaw_arm ,min_yaw_arm ,amplitude_yaw_arm ,roll_dumbbell ,pitch_dumbbell ,yaw_dumbbell ,max_roll_dumbbell ,max_picth_dumbbell ,min_roll_dumbbell ,min_pitch_dumbbell ,amplitude_roll_dumbbell ,amplitude_pitch_dumbbell ,total_accel_dumbbell ,var_accel_dumbbell ,avg_roll_dumbbell ,stddev_roll_dumbbell ,var_roll_dumbbell ,avg_pitch_dumbbell ,stddev_pitch_dumbbell ,var_pitch_dumbbell ,avg_yaw_dumbbell ,stddev_yaw_dumbbell ,var_yaw_dumbbell ,gyros_dumbbell_x ,gyros_dumbbell_y ,gyros_dumbbell_z ,accel_dumbbell_x ,accel_dumbbell_y ,accel_dumbbell_z ,magnet_dumbbell_x ,magnet_dumbbell_y ,magnet_dumbbell_z ,roll_forearm ,pitch_forearm ,yaw_forearm ,max_picth_forearm ,min_pitch_forearm ,amplitude_pitch_forearm ,total_accel_forearm ,var_accel_forearm ,gyros_forearm_x ,gyros_forearm_y ,gyros_forearm_z ,accel_forearm_x ,accel_forearm_y ,accel_forearm_z ,magnet_forearm_x ,magnet_forearm_y ,magnet_forearm_z ,classe))


# drop raw_timestamp_part_1 and raw_timestamp_part_2 from the training dataset, drop X
remaining_cols <- subset(remaining_cols, select = c(-X, -raw_timestamp_part_1, -raw_timestamp_part_2))

# Clean up dates
remaining_cols$cvtd_timestamp_clean <- as.Date(substr(remaining_cols$cvtd_timestamp,1,10), format='%d/%m/%Y')

# select user_name, classe, timestamp, mean(other variables) from table group by user_name, classe, timestamp

#aggregate(cbind(remaining_cols$user_name, remaining_cols$classe, remaining_cols$cvtd_timestamp ), remaining_cols$total_accel_arm  , mean)

install.packages("sqldf")
require(sqldf)

sqldf("select   user_name
                ,classe
                ,cvtd_timestamp_clean
                ,count(*) as num_rows
                ,avg(pitch_dumbbell) 
        from remaining_cols 
        group by user_name
                 ,classe
                 ,cvtd_timestamp_clean 
     
      ")
# Look at one user named adelmo
adelmo <- remaining_cols[with(which(user_name=='adelmo'), data=remaining_cols),]

adelmo_2 <- adelmo[order(adelmo$num_window),]

#
adelmo_full <- head(raw_train[with(which(user_name=='adelmo'), data=raw_train),], n=500L)


names(remaining_cols)[grepl('time', names(remaining_cols))]

head(remaining_cols$raw_timestamp_part_1)
head(remaining_cols$cvtd_timestamp)

train_sample <- raw_train[sample(nrow(raw_train), 1000),]

mod1 <- train(classe~ . , method='rf', preProcess='pca', data=train_sample) # Use bagging too! in trainControl()


max(remaining_cols[which(remaining_cols$user_name == 'adelmo' ),]$num_window)




df <- sqldf("select   user_name
                ,num_window
                ,case when new_window = 'yes' then 1 else 0 end as new_window
                ,count(*) as num_rows
                ,avg(pitch_dumbbell) as avg_pitch_dumbbell
        from remaining_cols 
        where user_name = 'adelmo'
        group by user_name
                ,num_window
                ,new_window
     
      ")

df2 <- sqldf("
        select 
                d.user_name
                ,d.num_window
                ,max(d.new_window) as new_window
                ,avg(avg_pitch_dumbbell) as avg_pitch_dumbbell
        from df d
        Group by d.user_name
                ,d.num_window
      
      ")


df3 <- sqldf("
        select 
                d.user_name
                ,d.num_window
                ,d.new_window
                ,e.num_window as num_window_2
                ,e.new_window as new_window_2
                ,(d.avg_pitch_dumbbell + e.avg_pitch_dumbbell)/2 as avg_pitch_dumbbell
        from df2 d
        inner join df e
        on d.user_name = e.user_name
        and d.num_window+1 = e.num_window
        and d.new_window+1 = e.new_window
      ")

and (case when d.new_window = 0 then 1 else 0 end) = e.new_window
x=1
ifelse(xor(x,1),1,0)
```

## Features to Use according to paper:
in the belt, were selected the mean and variance of the roll,
maximum, range and variance of the accelerometer vector,
variance of the gyro and variance of the magnetometer. In the arm, the variance of the accelerometer vector and the
maximum and minimum of the magnetometer were selected.
In the dumbbell, the selected features were the maximum of
the acceleration, variance of the gyro and maximum and
minimum of the magnetometer, while in the glove, the sum
of the pitch and the maximum and minimum of the gyro
were selected.

Preprocessing: 10 fold cross validation of 2.5 secs window chunk size
Algorithm: Random Forest
Ensemble: using Bagging
10 random forests each with 10 trees

reference: Qualitative Activity Recognition of Weight Lifting Exercises
Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th Augmented Human (AH) International Conference in cooperation with ACM SIGCHI (Augmented Human'13) . Stuttgart, Germany: ACM SIGCHI, 2013.

```{r}
# Features recommended by Paper
# belt:
# - Roll mean 
# - Roll variance 
# - accelerometer vector maximum
# - accelerometer vector range
# - accelerometer vector variance
# - gyro variance
# - magnetometer variance
# 
# Arm:
# - accelerometer variance vector 
# - magnetometer maximum 
# - magnetometer minimum
# 
# 
# Dumbbell:
# - acceleration vector maximum
# - gyro variance 
# - gyro maximum 
# - magnetometer minimum
# 
# Glove:
# - sum of the pitch 
# - gyro maximum  
# - gyro minimum


names(raw_train)
report_cols <- subset(raw_train , select=c(X ,user_name, raw_timestamp_part_1 ,raw_timestamp_part_2 ,cvtd_timestamp ,num_window, new_window ,avg_roll_belt ,var_roll_belt ,total_accel_belt ,gyros_belt_x ,gyros_belt_y ,gyros_belt_z  ,magnet_belt_x ,magnet_belt_y ,magnet_belt_z ,var_accel_arm ,magnet_arm_x ,magnet_arm_y ,magnet_arm_z ,total_accel_dumbbell ,gyros_dumbbell_x ,gyros_dumbbell_y ,gyros_dumbbell_z ,gyros_dumbbell_x ,gyros_dumbbell_y ,gyros_dumbbell_z ,magnet_dumbbell_x ,magnet_dumbbell_y,magnet_dumbbell_z ,pitch_forearm ,gyros_forearm_x  ,gyros_forearm_y  ,gyros_forearm_z   ,classe))

ncol(report_cols)



# Predictor Importance
varImp 
varImpPlot 
```


This section will use the features recommended by the report to train the model. These are contained in data frame 'report_cols'.

This section will try and group the records into an analytic record for training purposes.

Firstly it will try and count the amount of time each trial participant repeated each exercise.

```{r}
?subset
count(subset(report_cols, user_name == 'adelmo'), var=c('user_name', 'classe', 'num_window') )


# Turn report_cols into a data.table so you can aggregate
require(data.table)
report_cols_dt <- data.table(report_cols)

# Try and Roll up data 
roll_up <- report_cols_dt[, j=list( avg_roll_belt=mean(avg_roll_belt, na.rm = TRUE)
                         ,var_roll_belt=mean(var_roll_belt, na.rm = TRUE)
                         ,total_accel_belt_max=max(total_accel_belt)
                         ,total_accel_belt_range=(max(total_accel_belt) - min(total_accel_belt))
                         ,total_accel_belt_var = var(total_accel_belt)
                         ,gyro_variance=var(sqrt( gyros_belt_x^2 + gyros_belt_y^2 + gyros_belt_z^2))
                         ,var_accel_arm=var(var_accel_arm)
                         ,magnet_arm_max=max(sqrt(magnet_arm_x^2 + magnet_arm_y^2 + magnet_arm_z^2) )
                         ,magnet_arm_min=min(sqrt(magnet_arm_x^2 + magnet_arm_y^2 + magnet_arm_z^2) )
                         ,total_accel_dumbbell_max=max(total_accel_dumbbell)
                         ,gyros_dumbbell_var=var(sqrt(gyros_dumbbell_x^2 + gyros_dumbbell_y^2 + gyros_dumbbell_z^2 ))
                         ,gyros_dumbbell_max=max(sqrt(gyros_dumbbell_x^2 + gyros_dumbbell_y^2 + gyros_dumbbell_z^2 ))
                         ,magnet_dumbbell_min = min(sqrt(magnet_dumbbell_x^ +magnet_dumbbell_y^2 + magnet_dumbbell_z^2 ))
                         ,pitch_forearm_sum=sum(pitch_forearm)
                         ,gyros_forearm_max = max(sqrt(gyros_forearm_x^2 + gyros_forearm_y^2 + gyros_forearm_z^2   ))
                         ,gyros_forearm_min = min(sqrt(gyros_forearm_x^2 + gyros_forearm_y^2 + gyros_forearm_z^2   ))
                         
                         ), by = c('user_name','classe','num_window')]     
        
# Pick out the columns for training
# train_cols <- subset(report_cols, select=c(avg_roll_belt ,var_roll_belt ,total_accel_belt ,gyros_belt_x ,gyros_belt_y ,gyros_belt_z  ,magnet_belt_x ,magnet_belt_y ,magnet_belt_z ,var_accel_arm ,magnet_arm_x ,magnet_arm_y ,magnet_arm_z ,total_accel_dumbbell ,gyros_dumbbell_x ,gyros_dumbbell_y ,gyros_dumbbell_z ,magnet_dumbbell_x ,magnet_dumbbell_y,magnet_dumbbell_z ,pitch_forearm ,gyros_forearm_x  ,gyros_forearm_y  ,gyros_forearm_z   ,classe) )


train_cols <- data.frame(subset(roll_up, select=c(classe,avg_roll_belt ,var_roll_belt ,total_accel_belt_max ,total_accel_belt_range ,total_accel_belt_var  ,gyro_variance ,magnet_arm_max ,magnet_arm_min ,total_accel_dumbbell_max ,gyros_dumbbell_var ,gyros_dumbbell_max  ,pitch_forearm_sum ,gyros_forearm_max  ,gyros_forearm_min ) ))

names(train_cols)


require(functional)
train_cols$avg_roll_belt[!is.finite(train_cols$avg_roll_belt)] <- 0
train_cols$var_roll_belt[!is.finite(train_cols$var_roll_belt)] <- 0
train_cols$total_accel_belt_max[!is.finite(train_cols$total_accel_belt_max)] <- 0
train_cols$total_accel_belt_range[!is.finite(train_cols$total_accel_belt_range)] <- 0
train_cols$total_accel_belt_var[!is.finite(train_cols$total_accel_belt_var)] <- 0
train_cols$gyro_variance[!is.finite(train_cols$gyro_variance)] <- 0
#train_cols$var_accel_arm[!is.finite(train_cols$var_accel_arm)] <- 0
train_cols$magnet_arm_max[!is.finite(train_cols$magnet_arm_max)] <- 0
train_cols$magnet_arm_min[!is.finite(train_cols$magnet_arm_min)] <- 0
train_cols$total_accel_dumbbell_max[!is.finite(train_cols$total_accel_dumbbell_max)] <- 0
train_cols$gyros_dumbbell_var[!is.finite(train_cols$gyros_dumbbell_var)] <- 0
train_cols$gyros_dumbbell_max[!is.finite(train_cols$gyros_dumbbell_max)] <- 0
#train_cols$magnet_dumbbell_min[!is.finite(train_cols$magnet_dumbbell_min)] <- 0
train_cols$pitch_forearm_sum[!is.finite(train_cols$pitch_forearm_sum)] <- 0
train_cols$gyros_forearm_max[!is.finite(train_cols$gyros_forearm_max)] <- 0
train_cols$gyros_forearm_min[!is.finite(train_cols$gyros_forearm_min)] <- 0


nearZeroVar(train_cols, saveMetrics=TRUE)


#install.packages("ipred")

require(ipred)
# Train Model
mod2 <- train(classe~ . , method='rf', preProcess=c('bagImpute','pca'), trainControl(method='oob',number=10), data=train_cols) # Use bagging too! in trainControl

warnings()

# Print final model
print(mod2$finalModel)


# Make New Data
newData <- subset(raw_test, select=c(avg_roll_belt ,var_roll_belt ,total_accel_belt ,gyros_belt_x ,gyros_belt_y ,gyros_belt_z  ,magnet_belt_x ,magnet_belt_y ,magnet_belt_z ,var_accel_arm ,magnet_arm_x ,magnet_arm_y ,magnet_arm_z ,total_accel_dumbbell ,gyros_dumbbell_x ,gyros_dumbbell_y ,gyros_dumbbell_z ,magnet_dumbbell_x ,magnet_dumbbell_y,magnet_dumbbell_z ,pitch_forearm ,gyros_forearm_x  ,gyros_forearm_y  ,gyros_forearm_z   ,classe) )



# make newData 2
report_cols_test <- subset(raw_test , select=c(X ,user_name, raw_timestamp_part_1 ,raw_timestamp_part_2 ,cvtd_timestamp ,num_window, new_window ,avg_roll_belt ,var_roll_belt ,total_accel_belt ,gyros_belt_x ,gyros_belt_y ,gyros_belt_z  ,magnet_belt_x ,magnet_belt_y ,magnet_belt_z ,var_accel_arm ,magnet_arm_x ,magnet_arm_y ,magnet_arm_z ,total_accel_dumbbell ,gyros_dumbbell_x ,gyros_dumbbell_y ,gyros_dumbbell_z ,gyros_dumbbell_x ,gyros_dumbbell_y ,gyros_dumbbell_z ,magnet_dumbbell_x ,magnet_dumbbell_y,magnet_dumbbell_z ,pitch_forearm ,gyros_forearm_x  ,gyros_forearm_y  ,gyros_forearm_z   ,classe))

report_cols_test_dt <- data.table(report_cols_test)

# Try and Roll up data 
roll_up_test <- report_cols_test_dt[, j=list( avg_roll_belt=mean(avg_roll_belt, na.rm = TRUE)
                         ,var_roll_belt=mean(var_roll_belt, na.rm = TRUE)
                         ,total_accel_belt_max=max(total_accel_belt)
                         ,total_accel_belt_range=(max(total_accel_belt) - min(total_accel_belt))
                         ,total_accel_belt_var = var(total_accel_belt)
                         ,gyro_variance=var(sqrt( gyros_belt_x^2 + gyros_belt_y^2 + gyros_belt_z^2))
                         ,var_accel_arm=var(var_accel_arm)
                         ,magnet_arm_max=max(sqrt(magnet_arm_x^2 + magnet_arm_y^2 + magnet_arm_z^2) )
                         ,magnet_arm_min=min(sqrt(magnet_arm_x^2 + magnet_arm_y^2 + magnet_arm_z^2) )
                         ,total_accel_dumbbell_max=max(total_accel_dumbbell)
                         ,gyros_dumbbell_var=var(sqrt(gyros_dumbbell_x^2 + gyros_dumbbell_y^2 + gyros_dumbbell_z^2 ))
                         ,gyros_dumbbell_max=max(sqrt(gyros_dumbbell_x^2 + gyros_dumbbell_y^2 + gyros_dumbbell_z^2 ))
                         ,magnet_dumbbell_min = min(sqrt(magnet_dumbbell_x^ +magnet_dumbbell_y^2 + magnet_dumbbell_z^2 ))
                         ,pitch_forearm_sum=sum(pitch_forearm)
                         ,gyros_forearm_max = max(sqrt(gyros_forearm_x^2 + gyros_forearm_y^2 + gyros_forearm_z^2   ))
                         ,gyros_forearm_min = min(sqrt(gyros_forearm_x^2 + gyros_forearm_y^2 + gyros_forearm_z^2   ))
                         
                         ), by = c('user_name','classe','num_window')]  


# Score Data with Prediction
prediction <- predict( mod2, newdata=roll_up_test )

# See how well the model predicts
tt <- data.frame(prediction, raw_test$classe) 


```


```{r}
# explorartory
a <- unique(raw_train$cvtd_timestamp)
a[order(a)]


sqldf("
        select 
                d.user_name
                ,d.num_window
                ,d.new_window
                ,e.num_window as num_window_2
                ,e.new_window as new_window_2
                ,(d.avg_pitch_dumbbell + e.avg_pitch_dumbbell)/2 as avg_pitch_dumbbell
        from df2 d
        inner join df e
        on d.user_name = e.user_name
        and d.num_window+1 = e.num_window
        and d.new_window+1 = e.new_window
      ")



```



```{r}
# Take raw train and remove first seven attr

names(raw_train)

df <- subset(raw_train , select=c(roll_belt, pitch_belt, yaw_belt, total_accel_belt, kurtosis_roll_belt, kurtosis_picth_belt, kurtosis_yaw_belt, skewness_roll_belt, skewness_roll_belt.1, skewness_yaw_belt, max_roll_belt, max_picth_belt, max_yaw_belt, min_roll_belt, min_pitch_belt, min_yaw_belt, amplitude_roll_belt, amplitude_pitch_belt, amplitude_yaw_belt, var_total_accel_belt, avg_roll_belt, stddev_roll_belt, var_roll_belt, avg_pitch_belt, stddev_pitch_belt, var_pitch_belt, avg_yaw_belt, stddev_yaw_belt, var_yaw_belt, gyros_belt_x, gyros_belt_y, gyros_belt_z, accel_belt_x, accel_belt_y, accel_belt_z, magnet_belt_x, magnet_belt_y, magnet_belt_z, roll_arm, pitch_arm, yaw_arm, total_accel_arm, var_accel_arm, avg_roll_arm, stddev_roll_arm, var_roll_arm, avg_pitch_arm, stddev_pitch_arm, var_pitch_arm, avg_yaw_arm, stddev_yaw_arm, var_yaw_arm, gyros_arm_x, gyros_arm_y, gyros_arm_z, accel_arm_x, accel_arm_y, accel_arm_z, magnet_arm_x, magnet_arm_y, magnet_arm_z, kurtosis_roll_arm, kurtosis_picth_arm, kurtosis_yaw_arm, skewness_roll_arm, skewness_pitch_arm, skewness_yaw_arm, max_roll_arm, max_picth_arm, max_yaw_arm, min_roll_arm, min_pitch_arm, min_yaw_arm, amplitude_roll_arm, amplitude_pitch_arm, amplitude_yaw_arm, roll_dumbbell, pitch_dumbbell, yaw_dumbbell, kurtosis_roll_dumbbell, kurtosis_picth_dumbbell, kurtosis_yaw_dumbbell, skewness_roll_dumbbell, skewness_pitch_dumbbell, skewness_yaw_dumbbell, max_roll_dumbbell, max_picth_dumbbell, max_yaw_dumbbell, min_roll_dumbbell, min_pitch_dumbbell, min_yaw_dumbbell, amplitude_roll_dumbbell, amplitude_pitch_dumbbell, amplitude_yaw_dumbbell, total_accel_dumbbell, var_accel_dumbbell, avg_roll_dumbbell, stddev_roll_dumbbell, var_roll_dumbbell, avg_pitch_dumbbell, stddev_pitch_dumbbell, var_pitch_dumbbell, avg_yaw_dumbbell, stddev_yaw_dumbbell, var_yaw_dumbbell, gyros_dumbbell_x, gyros_dumbbell_y, gyros_dumbbell_z, accel_dumbbell_x, accel_dumbbell_y, accel_dumbbell_z, magnet_dumbbell_x, magnet_dumbbell_y, magnet_dumbbell_z, roll_forearm, pitch_forearm, yaw_forearm, kurtosis_roll_forearm, kurtosis_picth_forearm, kurtosis_yaw_forearm, skewness_roll_forearm, skewness_pitch_forearm, skewness_yaw_forearm, max_roll_forearm, max_picth_forearm, max_yaw_forearm, min_roll_forearm, min_pitch_forearm, min_yaw_forearm, amplitude_roll_forearm, amplitude_pitch_forearm, amplitude_yaw_forearm, total_accel_forearm, var_accel_forearm, avg_roll_forearm, stddev_roll_forearm, var_roll_forearm, avg_pitch_forearm, stddev_pitch_forearm, var_pitch_forearm, avg_yaw_forearm, stddev_yaw_forearm, var_yaw_forearm, gyros_forearm_x, gyros_forearm_y, gyros_forearm_z, accel_forearm_x, accel_forearm_y, accel_forearm_z, magnet_forearm_x, magnet_forearm_y, magnet_forearm_z, classe))

df_nzv <- nearZeroVar(df, saveMetrics=TRUE)
remaining <- df_nzv[which(df_nzv$nzv==FALSE),]

df_all_var <- subset(df , select=rownames(remaining))

# Remove Columsn with NAs
df_rm_na <- df_all_var[ , colSums(is.na(df_all_var)) == 0]

dim(df_all_var)
dim(df_rm_na )


# Find COrrelated variables and then remove extra variables
cor(subset(df_rm_na, select=-classe))


library(corrgram)

# Order = FALSE, panel.pie, panel.pts
corrgram(df_rm_na, order=FALSE, lower.panel=panel.shade,
         upper.panel=panel.pie, text.panel=panel.txt,
         col.regions=colorRampPalette(c("red","salmon","white","royalblue","navy")),
        
         main="Correlation of remaining features")

# train model

mod3 <- train(classe~ . , method='rf', preProcess=c('bagImpute','pca'), trainControl(method='oob',number=10), data=df_rm_na) # Use bagging too! in trainControl

 
```


