---
title: "Quiz 4"
author: "Andrew Szwec"
date: "28 April 2015"
output: html_document
---

## Question 1
```{r}
setwd("~/Documents/Coursera/dataScienceSpecialisation/pracML/quiz/quiz4")

library(ElemStatLearn)
?vowel.train
data(vowel.train)
data(vowel.test) 

set.seed(33833)

vowel.train$y <- as.factor(vowel.train$y)
vowel.test$y <- as.factor(vowel.test$y)

library(caret)

inTrain = createDataPartition(vowel.train$y, p = 0.7)[[1]]
training = vowel.train[ inTrain,]     # 70% of records
testing = vowel.train[-inTrain,]      # 30% of reocrds

mod1 <- train(y~. , mehtod="rf", data=vowel.train )
mod2 <- train(y~. , mehtod="gbm", data=vowel.train )

rf acc = 0.9358227
gbm acc = 0.9364548


save(mod1, file = "mod1_001.RData")
save(mod2, file = "mod2_001.RData")

print(mod1$finalModel)
print(mod2$finalModel)

predv1 <- predict(mod1, vowel.test )
predv2 <- predict(mod2, vowel.test )

length(predv1[which(predv1 == vowel.test$y)])/length(vowel.test$y)
# 0.5952381
length(predv2[which(predv2 == vowel.test$y)])/length(vowel.test$y)
# 0.61


```


## View Confusion matrix for random forest
```{r}
      confusionMatrix(predv1, vowel.test$y)
```
0.5952


## View Confusion matrix for random forest
```{r}
      confusionMatrix(predv2, vowel.test$y)
```
0.6126

# Question 2
```{r}
library(caret)
library(gbm)
set.seed(3433)
library(AppliedPredictiveModeling)
data(AlzheimerDisease)
adData = data.frame(diagnosis,predictors)
inTrain = createDataPartition(adData$diagnosis, p = 3/4)[[1]]
training = adData[ inTrain,]
testing = adData[-inTrain,]

set.seed(62433)


mod_rf <- train(diagnosis~. , mehtod="rf", data=training )
mod_gbm <- train(diagnosis~. , mehtod="gbm", data=training )
mod_lda <- train(diagnosis~. , mehtod="lda", data=training )

save(mod_rf, file = "mod_rf_001.RData")
save(mod_gbm, file = "mod_gbm_001.RData")
save(mod_lda, file = "mod_lda_001.RData")

pred1 <- predict(mod_rf, testing )
pred2 <- predict(mod_gbm, testing )
pred3 <- predict(mod_lda, testing )

df2 <- data.frame(pred1, pred2, pred3, diagnosis=testing$diagnosis)
head(df2)

mod_fn <- train(diagnosis~. , mehtod="rf", data=df2 )
mod_fn$finalModel
# 0.7605741
# Predict using the ensemble
pred_fn <- predict(mod_fn, testing )
```
## View Confusion matrix for ensemble
```{r}
      confusionMatrix(pred_fn, testing$diagnosis)
      # From confusion matrix
      tp <- 11
      tn <- 54
      fp <- 6
      fn <- 11
      acc1 <- (tp+tn)/(tp+fp+fn+tn)
```
## Accuracy of ensemble on test set is ...
```{r}
acc1
```

## View Confusion matrix for random forest
```{r}
      confusionMatrix(pred1, testing$diagnosis)
      # From confusion matrix
      tp <- 11
      tn <- 52
      fp <- 8
      fn <- 11
      acc_rf <- (tp+tn)/(tp+fp+fn+tn)
```
## Accuracy of random forest on test set is ...
```{r}
acc_rf
```

## View Confusion matrix for gbm
```{r}
      confusionMatrix(pred2, testing$diagnosis)
      # From confusion matrix
      tp <- 11
      tn <- 54
      fp <- 6
      fn <- 11
      acc_gbm <- (tp+tn)/(tp+fp+fn+tn)
```
## Accuracy of gbm on test set is ...
```{r}
acc_gbm
```

## View Confusion matrix for lda
```{r}
      confusionMatrix(pred3, testing$diagnosis)
      # From confusion matrix
      tp <- 10
      tn <- 54
      fp <- 6
      fn <- 12
      acc_lda <- (tp+tn)/(tp+fp+fn+tn)
```
## Accuracy of lda on test set is ...
```{r}
acc_lda
```

```{r}
acc1
acc_rf
acc_gbm
acc_lda

```
### Therefore ensemble accuracy is 0.79 and is same as GBM

#Question 3
```{r}
require(caret)
set.seed(3523)
library(AppliedPredictiveModeling)
data(concrete)
inTrain = createDataPartition(concrete$CompressiveStrength, p = 3/4)[[1]]
training = concrete[ inTrain,]
testing = concrete[-inTrain,]

set.seed(233)

mod_lasso <- train(CompressiveStrength~.,method="lasso", data=training   )
print(mod_lasso$finalModel)
plot.enet(mod_lasso$finalModel)



?plot.enet
require(elasticnet)
mod_enet <- enet(x=training, y=CompressiveStrength, lambda=100)

?lars
lars::lars(training, CompressiveStrength, type="lasso", ) 

sapply(mod_lasso, function(x) names(x))
```

# Question 4
```{r}
library(lubridate)  # For year() function below
dat = read.csv("/Users/andrewszwec/Documents/Coursera/dataScienceSpecialisation/pracML/quiz/quiz4/gaData.csv")
training = dat[year(dat$date) < 2012,]
testing = dat[(year(dat$date)) > 2011,]
tstrain = ts(training$visitsTumblr)
tstest  = ts(testing$visitsTumblr)
      

dim(dat)
600
nrow(training)
365
nrow(testing)
235

?forecast
plot(tstrain)
    
require(forecast)

# Fit Model
fit <- bats(tstrain )
myforecast <- forecast(fit, h=235)
plot(myforecast)


actual <- testing$visitsTumblr[]
hi95 <- myforecast$upper[,2]
lo95 <- myforecast$lower[,2]

require(data.table)
dt1 <- data.table(lo95, hi95, actual)


```

# Question 5
```{r}
set.seed(3523)
library(AppliedPredictiveModeling)
data(concrete)
inTrain = createDataPartition(concrete$CompressiveStrength, p = 3/4)[[1]]
training = concrete[ inTrain,]
testing = concrete[-inTrain,]


set.seed(325)
require(e1071)

?svm
svm1 <- svm(CompressiveStrength~., data=training)

pred1 <- predict(svm1, newdata=testing)

#install.packages("Metrics")
require(Metrics)
rmse(actual=testing$CompressiveStrength, predicted=pred1)


length(testing$CompressiveStrength)
length(pred1)
```


